% To show solutions, compile with:
%   latex "\let\showsolutions\relax\input{filename}"

\documentclass{article}
\input{bridge}
\begin{document}
Topics covered:
Jacoby transfers
\begin{problemset}
\problem{  \deal{South}{None}%
    {\hand{K\,2}{Q\,5\,3}{A\,K\,J\,9\,6}{K\,J\,9}}%
    {\hand{Q\,J\,10\,9}{8\,6\,4}{5}{A\,Q\,7\,5\,4}}%
    {\hand{8\,7\,5\,4\,3}{A\,K\,J\,7\,2}{7\,4}{2}}%
    {\hand{A\,6}{10\,9}{Q\,10\,8\,3\,2}{10\,8\,6\,3}}
%
}{%
  \begin{bidding}
    &&&Pass\\
    Pass&1\nt{}&Pass&??
  \end{bidding}%
}{%
2\d{}%
}{%
Partner has opened a strong 1\nt{}. With 5--5 in the majors and invitational strength, first make a Jacoby transfer into hearts, and then bid 2\s{} afterwards. Partner will then have the options of passing 2\s{} with a minimum hand and a spade fit, bidding 3\h{} with a minimum hand and no spade fit (in which case a heart fit is guaranteed), or bidding one of the majors at the 4 level with a maximum. This wrong-sides the contract when the 1\nt{} bidder has a doubleton heart.%
}
\problem{  \deal{West}{N/S}%
    {\hand{A\,K\,4}{10\,9\,3}{A\,K\,J\,9\,4}{7\,6}}%
    {\hand{9\,8\,3}{K\,8\,6\,4}{5\,2}{J\,8\,3\,2}}%
    {\hand{Q\,J\,6\,5\,2}{J\,5\,2}{10\,3}{A\,K\,5}}%
    {\hand{10\,7}{A\,Q\,7}{Q\,8\,7\,6}{Q\,10\,9\,4}}
%
}{%
  \begin{bidding}
    Pass&1\nt{}&Pass&??
  \end{bidding}%
}{%
2\h{}%
}{%
Partner has opened a strong 1\nt{}. You have a balanced hand with game-going but not slam-going strength, and a 5-card major. Make a Jacoby transfer into the suit, then bid 3\nt{}. This gives partner the options of passing and playing in notrump with 2-card spade support or correcting to 4\s{} with a fit, knowing that you belong in game but not slam.%
}
\problem{  \deal{North}{E/W}%
    {\hand{J\,10\,9\,8\,7}{K\,Q}{3}{Q\,J\,9\,3\,2}}%
    {\hand{6\,4}{8\,6\,4\,2}{A\,J\,10\,5\,4}{6\,4}}%
    {\hand{K\,2}{A\,7\,5\,3}{Q\,8\,7\,2}{A\,K\,10}}%
    {\hand{A\,Q\,5\,3}{J\,10\,9}{K\,9\,6}{8\,7\,5}}
%
}{%
  \begin{bidding}
    &Pass&Pass&1\nt{}\\
    Pass&2\h{}&Pass&??
  \end{bidding}%
}{%
2\s{}%
}{%
You have opened a strong 1\nt{}, and partner has made a Jacoby transfer, indicating they have at least 5 spades. Even though you only have 2-card support, complete the transfer by bidding the next higher suit. You have at least a 7-card fit. If partner is very weak, 2\s{} rates to play better than notrump, and you want to be declarer so that your strong hand stays hidden. If partner has at least invitational strength, he will make another bid to give you options of where to play.%
}
\problem{  \deal{North}{N/S}%
    {\hand{A\,Q\,8\,3}{K\,J\,3}{6\,5\,3}{A\,J\,6}}%
    {\hand{J\,9\,6}{Q\,10\,7\,2}{Q\,10\,7}{10\,8\,2}}%
    {\hand{K\,10\,7\,4\,2}{A\,9\,5}{9\,2}{Q\,5\,4}}%
    {\hand{5}{8\,6\,4}{A\,K\,J\,8\,4}{K\,9\,7\,3}}
%
}{%
  \begin{bidding}
    &1\nt{}&Pass&??
  \end{bidding}%
}{%
2\h{}%
}{%
Partner has opened a strong 1\nt{}. You have a balanced hand with invitational strength, and a 5-card major. Make a Jacoby transfer into the suit, then bid 2\nt{}. This gives partner the options of playing in notrump with 2-card spade support  or in spades with a fit, and the option of playing in partscore with a minimum hand and game with a maximum.%
}
\problem{  \deal{North}{Both}%
    {\hand{J\,9}{10\,9\,8\,4\,2}{Q\,9\,4\,2}{A\,7}}%
    {\hand{8\,5\,3}{Q\,5\,3}{10\,8\,7}{K\,Q\,8\,6}}%
    {\hand{A\,Q\,4}{A\,J}{K\,6\,5\,3}{J\,10\,9\,4}}%
    {\hand{K\,10\,7\,6\,2}{K\,7\,6}{A\,J}{5\,3\,2}}
%
}{%
  \begin{bidding}
    &Pass&Pass&1\nt{}\\
    Pass&2\d{}&Pass&??
  \end{bidding}%
}{%
2\h{}%
}{%
You have opened a strong 1\nt{}, and partner has made a Jacoby transfer, indicating they have at least 5 hearts. Even though you only have 2-card support, complete the transfer by bidding the next higher suit. You have at least a 7-card fit. If partner is very weak, 2\h{} rates to play better than notrump, and you want to be declarer so that your strong hand stays hidden. If partner has at least invitational strength, he will make another bid to give you options of where to play.%
}
\problem{  \deal{East}{N/S}%
    {\hand{A\,10\,9\,8\,2}{Q\,10\,9}{A\,K\,10\,9}{J}}%
    {\hand{K\,J\,5\,4}{K\,8\,6}{J\,7\,6}{8\,7\,3}}%
    {\hand{Q\,3}{A\,7\,3}{Q\,5\,4}{A\,K\,10\,6\,5}}%
    {\hand{7\,6}{J\,5\,4\,2}{8\,3\,2}{Q\,9\,4\,2}}
%
}{%
  \begin{bidding}
    &&Pass&1\nt{}\\
    Pass&2\h{}&Pass&??
  \end{bidding}%
}{%
2\s{}%
}{%
You have opened a strong 1\nt{}, and partner has made a Jacoby transfer, indicating they have at least 5 spades. Even though you only have 2-card support, complete the transfer by bidding the next higher suit. You have at least a 7-card fit. If partner is very weak, 2\s{} rates to play better than notrump, and you want to be declarer so that your strong hand stays hidden. If partner has at least invitational strength, he will make another bid to give you options of where to play.%
}
\problem{  \deal{North}{E/W}%
    {\hand{A\,7}{J\,10\,2}{A\,J\,10\,5\,3}{A\,K\,5}}%
    {\hand{J\,10\,3}{K\,8\,7}{K\,6}{10\,8\,6\,4\,2}}%
    {\hand{K\,Q\,9\,6\,4}{6\,5\,3}{Q\,4}{J\,9\,7}}%
    {\hand{8\,5\,2}{A\,Q\,9\,4}{9\,8\,7\,2}{Q\,3}}
%
}{%
  \begin{bidding}
    &1\nt{}&Pass&??
  \end{bidding}%
}{%
2\h{}%
}{%
Partner has opened a strong 1\nt{}. You have a balanced hand with invitational strength, and a 5-card major. Make a Jacoby transfer into the suit, then bid 2\nt{}. This gives partner the options of playing in notrump with 2-card spade support  or in spades with a fit, and the option of playing in partscore with a minimum hand and game with a maximum.%
}
\problem{  \deal{South}{N/S}%
    {\hand{K\,10\,4}{Q\,7\,4}{A\,K\,8\,5\,4}{A\,10}}%
    {\hand{7\,3}{A\,K\,10\,8\,6}{Q\,J\,7\,6\,2}{9}}%
    {\hand{Q\,9\,8\,5\,2}{2}{10\,9}{Q\,J\,7\,6\,2}}%
    {\hand{A\,J\,6}{J\,9\,5\,3}{3}{K\,8\,5\,4\,3}}
%
}{%
  \begin{bidding}
    &&&Pass\\
    Pass&1\nt{}&Pass&??
  \end{bidding}%
}{%
2\h{}%
}{%
Partner has opened a strong 1\nt{}. You have such a weak hand that you have no interest in game, but you do have a 5-card major. Playing in it, even if it's a 5-2 fit, is more likely to succeed than playing in notrump. Make a Jacoby transfer into the suit, then pass and leave partner at the 2 level.%
}
\problem{  \deal{West}{Both}%
    {\hand{2}{10\,8\,4\,3\,2}{A\,6\,5}{A\,J\,9\,5}}%
    {\hand{A\,J\,9\,6\,4}{9\,7}{10\,9\,4\,2}{6\,3}}%
    {\hand{K\,Q\,10\,8}{A\,K\,6}{J\,7\,3}{K\,10\,2}}%
    {\hand{7\,5\,3}{Q\,J\,5}{K\,Q\,8}{Q\,8\,7\,4}}
%
}{%
  \begin{bidding}
    Pass&Pass&Pass&1\nt{}\\
    Pass&2\d{}&Pass&??
  \end{bidding}%
}{%
2\h{}%
}{%
You have opened a strong 1\nt{}, and partner has made a Jacoby transfer. Complete the transfer by bidding the next higher suit. Partner promises at least 5 cards in that major, but wants you to be declarer so your stronger hand stays hidden.%
}
\problem{  \deal{West}{E/W}%
    {\hand{Q\,8\,2}{K\,Q\,9\,4}{J\,3}{A\,K\,7\,3}}%
    {\hand{7\,4\,3}{A}{A\,K\,8\,7\,6}{J\,9\,5\,2}}%
    {\hand{A\,9\,6}{J\,10\,5\,3\,2}{Q\,2}{Q\,8\,6}}%
    {\hand{K\,J\,10\,5}{8\,7\,6}{10\,9\,5\,4}{10\,4}}
%
}{%
  \begin{bidding}
    Pass&1\nt{}&Pass&??
  \end{bidding}%
}{%
2\d{}%
}{%
Partner has opened a strong 1\nt{}. You have a balanced hand with invitational strength, and a 5-card major. Make a Jacoby transfer into the suit, then bid 2\nt{}. This gives partner the options of playing in notrump with 2-card heart support  or in hearts with a fit, and the option of playing in partscore with a minimum hand and game with a maximum.%
}
\end{problemset}
\end{document}
